Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-15 WRITEUP/ms.tex
fig 5 caption

\begin{figure*}
\centering
\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top),
{\bf .... (middle), and blah blah (bottom)}
for MCs (star symbols)
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). 
\label{fig:larsons_single}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top),
$\alpha_{\rm vir}$-mass relation 
(middle), and 
$\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom)
for MCs (star symbols)
identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). 
\label{fig:larsons_single}}
\end{figure*}
